Wu-Tang Clan

### 2015-03-03 rmtw/a5/latex8.tex
DSA

Volter et al\cite{volter2013model} says that successful adoption of MDSD should increase development speed, increase software quality, improve reusability and improve manageability through abstraction.

@@

Academia appears to be united in the opinion that MDSD is an improvement compared with traditional software development \cite{staron2006adopting} \cite{volter2013model}. However, why do many large software companies chose not to adopt MDSD?

@@

It is important to note that did not perform either a Systematic Mapping Study nor a Tertiary Review of existing literature. There was sufficient evidence in existence for the applicability of MDSD such that we could rule out the need to perform a Systematic Mapping Study. Furthermore, there were insufficient SLRs that had been conducted prior to our study, thus, a Tertiary Review was not possible nor appropriate at that time.

@@

To ensure that our search criteria had be selected correctly, a small trial study was performed to ensure that our criteria could find six predetermined and well known papers which are relevant to our study. %Cite the papers here?

While Kitchenham\cite{kitchenham2007guidelines} suggest the inclusion of papers from related disciplines, this was not undertaken for this study. Other disciplines, while appropriate for some research we shall review, are not appropriate or relevant.

As suggested by Kitchenham\cite{kitchenham2007guidelines}, publication bias is something that we will have to overcome in our study. From our trial study and previous research into related work, it became clear that there seems to exist some bias towards the adoption of MDSD; there are few papers which speak ill of it. To help alleviate this we shall check, but not include, grey literature (non-formally published papers), conference proceedings. We shall also attempt to contact researchers and change agents with experience of implementing MDSD to ascertain if they have unpublished results which can balance the positive bias.

@@

The digital libraries, mentioned in section Table 1, were chosen for their extensive catalogues, reliability and availability of the data. Hand searching of journals was not performed as we decided to limit the scope of the search to digital libraries, conferences and other sources.

@@

The selection criteria for the papers was further refined during this stage. After applying the initial exclusion and inclusion criteria, exclusions and inclusions were based on practicality. Below is a short list of these criteria.

@@

The Quality of the papers was also considered before they were examined for use in the study. Determination of paper quality occurred after initial exclusions and inclusions had been performed. These additional quality checks sought to eliminate papers with excessive bias, low quality and the unreliable results.

@@

To assess the reliability of the inclusions and exclusions, Fleiss' kappa index was applied on both researchers findings. All conflicts regarding to acceptance of papers was discussed and resolved prior to their inclusion in the SLR. The initial kappa rating achieved was 0.78, which lies in the band 0.61 - 0.80 indicating a strong alignment between the researchers.

@@

>>>>

Volter et al. \cite{volter2013model} state that successful adoption of MDSD should increase development speed, increase software quality, improve reusability and improve manageability through abstraction.

@@

Academia appears to be united in the opinion that MDSD is an improvement compared with traditional software development \cite{staron2006adopting} \cite{volter2013model}. However, why do many large software companies choose to not adopt MDSD?

@@

It is important to note that did not perform either a Systematic Mapping Study nor a Tertiary Review of (XXX cite?) existing literature. There was sufficient evidence in existence for the applicability of MDSD such that we could rule out the need to perform a Systematic Mapping Study. Furthermore, there were insufficient SLRs that had been conducted prior to our study, thus, a Tertiary Review \cite{kitchenham2007guidelines} was not possible nor appropriate at that time.

@@

To ensure that our search criteria had be meaningfully defined, a small trial study was performed to guarantee that our criteria could find six predetermined and well known papers which are relevant to our study. As Kitchenham \cite{kitchenham2007guidelines} suggests, papers from other disciplines will be included in the literature review.

Possible publication bias was taken into account during the study. From our trial study and previous research into related work, it became clear that there existed bias towards the adoption of MDSD; there were few papers which spoke ill of it. To help alleviate this we checked, but did not include, grey literature (non-formally published papers) and conference proceedings. We also contacted researchers and change agents with experience of implementing MDSD to discover if they had unpublished results which could balance the positive bias.

@@

The digital libraries, mentioned in Table 1, were chosen for their extensive catalogues, reliability and availability of the data. Hand searching of journals was not performed as we decided to limit the scope of the search to digital libraries, conferences and other sources.

@@

The selection criteria for the papers were refined during this stage. After applying the initial exclusion and inclusion criteria, exclusions and inclusions were based on practicality. Below is a short list of these criteria.

@@

The quality of the papers was also considered before they were examined for use in the study. Determination of paper quality occurred after initial exclusions and inclusions had been performed. These additional quality checks sought to eliminate papers with excessive bias, low quality and the unreliable results.

@@

To assess the reliability of the inclusions and exclusions, Fleiss' Kappa index was applied on both researchers findings. All conflicts regarding to acceptance of papers was discussed and resolved prior to their inclusion in the SLR. The initial Kappa rating achieved was 0.78, which lies in the band 0.61 - 0.80 indicating a strong alignment between the researchers.

@@

Parts Section 1.2 have been re-used from previous assignments. Because of this, the paper may show up on Urkund.
